Causal Inference with Graphical Neural Networks

### 2024-04-19 latex/draft.tex
intro and related work

\section{Introduction}
\label{intro}

>>>>

\section{Introduction}
\label{intro}
Neural networks are at the center of computer science research and have revolutionized our ability to model complex relationships with data.
However, as these networks become increasingly pervasive in decision-making processes, understanding the causality behind their predictions becomes paramount. 
The distinction between correlation and causation is not merely philosophical; it's foundational for building robust, interpretable, and ethically sound AI systems.

Causal inference, a field deeply rooted in statistics and philosophy, offers a framework to disentangle cause-and-effect relationships from observed data. 
Traditionally, causal inference has been applied in fields such as epidemiology, economics, and social sciences. 
However, its integration into the domain of neural networks presents a promising frontier, with implications ranging from improving model interpretability to enhancing the fairness and accountability of AI systems.

In this paper, we explore the intersection of causal inference and neural networks, focusing on the application of Graph Neural Networks (GNNs) to causal modeling.
We leverage the power of GNNs to learn representations of graph-structured data and perform a supervised classification task on the LUCAS0 dataset~\cite{lucas_dataset}.
Our goal is to demonstrate the effectiveness of GNNs in capturing causal relationships within a graph and to provide insights into the interpretability and robustness of these models.

\section{Related Work}
\label{related}
The integration of causal inference with neural networks has garnered significant interest in recent years.
Several approaches have been proposed to combine the strengths of these two fields, with a particular focus on leveraging the expressive power of neural networks to model causal relationships.
Koch et al. discusses ongoing work to extend causal inference to settings where confounding is non-linear, time-varying, or encoded in text, networks, and images \cite{koch2023deep}.
Also, Yuan et al. compared the performance of CNN's on causal data to previous methods \cite{yuan2020causal}.
